---
title: "deseq2_sleuth_analysis_210423"
author: "Changhua Yu"
date: "4/23/2021"
output: html_document
---

# Description
- This markdown file is intended to perform an integrative analysis on the 
following 3 RNA-Seq analysis pipelines:
1. STAR mapping --> DESeq2 for DE genes
2. kallisto mapping --> sleuth for DE genes
3. salmon mapping --> sleuth for DE genes 

The following analysis would be performed:
1. For Amputation VS Pre-Amputation DE genes, inspect the overlapping extent and
the "most confident" genes overlapped within the 3 methods
2. For Regenerating VS Non-Regenerating DE genes, inspect the overlapping extent 
and the "most confident" genes overlapped within the 3 methods

### Load packages
```{r}
# Load library
library(ggvenn)
```

### Read in differential gene lists and count matrix from all three pipelines
```{r}
res.ampu.sig.do = read.csv("../out/210205/res.ampu.sig.do.csv")
res.ampu.sig.up = read.csv("../out/210205/res.ampu.sig.up.csv")
res.rege.sig.up = read.csv("../out/210205/res.rege.sig.up.csv")
res.rege.sig.do = read.csv("../out/210205/res.rege.sig.do.csv")
kallisto.ampu.sig = read.csv("../out/210423/kallisto/cut.vs.blank.sig.csv")
kallisto.rege.sig = read.csv("../out/210423/kallisto/reg.sig.csv")
salmon.ampu.sig = read.csv("../out/210423/salmon/cut.vs.blank.sig.csv")
salmon.rege.sig = read.csv("../out/210423/salmon/reg.sig.csv")
```

### Separate the up-regulation and down-regulation in the sleuth pipeline
```{r}
kallisto.count.matrix = read.csv("../out/210423/kallisto/count_matrix.csv")
salmon.count.matrix = read.csv("../out/210423/salmon/count_matrix.csv",row.names = 1)
```

```{r}
kallisto.ampu.sig
```

```{r}
x <- list(
  res.ampu.sig.up = res.ampu.sig.up$gene, 
  kallisto.ampu.sig = kallisto.ampu.sig$target_id,
  salmon.ampu.sig = salmon.ampu.sig$target_id
  )

ggvenn(
  x, 
  fill_color = c("#0073C2FF", "#EFC000FF","#868686FF"),
  stroke_size = 0.5, set_name_size = 4
  )
```
```{r}
common.ampu.up = intersect(intersect(res.ampu.sig.up$gene, kallisto.ampu.sig$target_id),salmon.ampu.sig$target_id)
```

```{r}
x <- list(
  res.ampu.sig.do = res.ampu.sig.do$gene, 
  kallisto.ampu.sig = kallisto.ampu.sig$target_id,
  salmon.ampu.sig = salmon.ampu.sig$target_id
  )

ggvenn(
  x, 
  fill_color = c("#0073C2FF", "#EFC000FF","#868686FF"),
  stroke_size = 0.5, set_name_size = 4
  )
```

```{r}
common.ampu.do = intersect(intersect(res.ampu.sig.do$gene, kallisto.ampu.sig$target_id),salmon.ampu.sig$target_id)
```

```{r}
x <- list(
  res.rege.sig.up = res.rege.sig.up$gene, 
  kallisto.rege.sig = kallisto.rege.sig$target_id,
  salmon.rege.sig = salmon.rege.sig$target_id
  )

ggvenn(
  x, 
  fill_color = c("#0073C2FF", "#EFC000FF","#868686FF"),
  stroke_size = 0.5, set_name_size = 4
  )
```

```{r}
common.rege.up = intersect(intersect(res.rege.sig.up$gene, kallisto.rege.sig$target_id),salmon.rege.sig$target_id)
```

```{r}
x <- list(
  res.rege.sig.do = res.rege.sig.do$gene, 
  kallisto.rege.sig = kallisto.rege.sig$target_id,
  salmon.rege.sig = salmon.rege.sig$target_id
  )

ggvenn(
  x, 
  fill_color = c("#0073C2FF", "#EFC000FF","#868686FF"),
  stroke_size = 0.5, set_name_size = 4
  )
```

```{r}
common.rege.do = intersect(intersect(res.rege.sig.do$gene, kallisto.rege.sig$target_id),salmon.rege.sig$target_id)
```

### Export out the common overlapping gene lists
```{r}
write.csv(common.ampu.up,"../out/210423/common.ampu.up.csv")
write.csv(common.ampu.do,"../out/210423/common.ampu.do.csv")
write.csv(common.rege.up,"../out/210423/common.rege.up.csv")
write.csv(common.rege.do,"../out/210423/common.rege.do.csv")
```



